Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-14 paper.tex
cite Bergstra paper
some work on the conclusions

In \sklearn, both \texttt{GridSearchCV} and \texttt{RandomizedSearchCV} meta-estimators
implement model selection. They take as inputs an estimator (basic or
complex), a grid of hyper-parameter values, a cross-validation scheme and a
score function. At \texttt{fit}, a \texttt{GridSearchCV} object generates
exhaustively all hyper-parameter combinations from the grid, while a
\texttt{RandomizedSearchCV} instance generates a limited number of combinations
randomly sampled from the grid. Then, for each combination, the meta-estimator
fits the given estimator with the corresponding hyper-parameter values and
evaluates its performance through the given cross-validation scheme. Finally,
the best performing model is retained and exposed as a public attribute.

@@

ToDo.

\subsection{Future work}

The \sklearn toolkit is by no means finished,
although it is coming close to a 1.0 release.

\sklearn does not support all tasks in the broad field of machine learning,
and does not intend to either;
in particular, structured prediction and bandit-style online learning algorithms
are considered ``off-topic'' for the library,
and submissions of implementations of these for inclusion
will (at least at present) be rejected.
Collaborative filtering algorithms are not implemented
and it is remains to be seen
whether an API for them can be designed that matches the \sklearn API.

At a lower-level, a potential point of improvement
is parallel processing, which, as described in Section~\ref{sec:parallel},
is only implemented at a rather coarse-grained level.
Cython's built-in support for OpenMP \citep{dagum1998openmp}
remains a viable candidate technology
for more fine-grained multicore support in \sklearn.

>>>>

In \sklearn, both \texttt{GridSearchCV} and \texttt{RandomizedSearchCV} meta-estimators
implement model selection. They take as inputs an estimator (basic or
complex), a grid of hyper-parameter values, a cross-validation scheme and a
score function. At \texttt{fit}, a \texttt{GridSearchCV} object generates
exhaustively all hyper-parameter combinations from the grid, while a
\texttt{RandomizedSearchCV} instance generates a limited number of combinations
randomly sampled from the grid \citep{bergstra2012}. Then, for each combination, the meta-estimator
fits the given estimator with the corresponding hyper-parameter values and
evaluates its performance through the given cross-validation scheme. Finally,
the best performing model is retained and exposed as a public attribute.

@@

\textcolor{red}{TODO: include some overall conclusions (e.g., reasons of the success sklearn)}

Although it is coming close to a 1.0 release, the \sklearn toolkit is by no
means finished. At the time, it does not support all tasks in the broad field of
machine learning, but does not intend to either. Among others, missing features
include neural networks, ensemble meta-estimators for bagging or subsampling
strategies, or missing value completion algorithms provided as transformers.
However, topics like structured prediction or reinforcement learning are
considered off-topic for the project. The library also does not provide any
collaborative filtering algorithms -- it remains to be seen whether a compatible
and matching API can be written for them.

At a lower-level, a potential point of improvement is parallel processing,
which, as described in Section~\ref{sec:parallel}, is only implemented at a
rather coarse-grained level. Cython built-in support for OpenMP
\citep{dagum1998openmp} remains a viable candidate technology for more fine-
grained multicore support in \sklearn.
